Bayesian Shape Reconstruction and Optimal Guidance for Autonomous Landing on Asteroids

### 2019-03-05 manuscript.tex
Move even more figures

\begin{figure}[htbp]
    \centering
    \subcaptionbox{Initial Shape Estimate\label{fig:castalia_partial_weights_0}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_1.jpg}}%
    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:castalia_partial_weights_25}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_3749.jpg}}%
    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:castalia_partial_weights_50}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_7499.jpg}}

    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:castalia_partial_weights_75}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_11249.jpg}}%
    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:castalia_partial_weights_100}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_14998.jpg}}%
    \subcaptionbox{True Shape Model\label{fig:castalia_weights_truth}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/mesh_update/castalia/truth.jpg}}
    \caption[Asteroid Castalia shape reconstruction with uncertainty]{Incremental reconstruction of asteroid Castalia. The images colored according to the shape uncertainty. Areas of high uncertainty are in yellow while ares of low uncertainty are in purple.~\label{fig:castalia_weights_reconstruction}}
\end{figure}

>>>>

\begin{figure}[htbp]
    \centering
    \subcaptionbox{Initial Shape Estimate\label{fig:castalia_partial_weights_0}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{dynamic_exploration_castalia_partial_weights_1.jpg}}%
    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:castalia_partial_weights_25}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{dynamic_exploration_castalia_partial_weights_3749.jpg}}%
    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:castalia_partial_weights_50}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{dynamic_exploration_castalia_partial_weights_7499.jpg}}

    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:castalia_partial_weights_75}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{dynamic_exploration_castalia_partial_weights_11249.jpg}}%
    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:castalia_partial_weights_100}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{dynamic_exploration_castalia_partial_weights_14998.jpg}}%
    \subcaptionbox{True Shape Model\label{fig:castalia_weights_truth}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{mesh_update_castalia_truth.jpg}}
    \caption[Asteroid Castalia shape reconstruction with uncertainty]{Incremental reconstruction of asteroid Castalia. The images colored according to the shape uncertainty. Areas of high uncertainty are in yellow while ares of low uncertainty are in purple.~\label{fig:castalia_weights_reconstruction}}
\end{figure}
